---
title: "test"
author: Matteo Manca
output: 
  ioslides_presentation: 
    incremental: yes
    keep_md: yes
    smaller: yes
    transition: slower
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r, echo=FALSE}
library(plotly)
```

## Slide with R Code and Output

```{r, plotly=TRUE}

set.seed(100)
d <- diamonds[sample(nrow(diamonds), 1000), ]
head(d)
p <- ggplot(data = d, aes(x = carat, y = price)) +
  geom_point(aes(text = paste("Clarity:", clarity)), size = 2) +
  geom_smooth(aes(colour = cut, fill = cut)) + facet_wrap(~ cut)

gg <- ggplotly(p)

```

## Slide with R Code and Output

```{r, plotly=TRUE}
gg
```

## Slide with Plot

```{r}

```

