---
output: 
  html_document: 
    keep_md: yes
---

# Chord diagram

This script generates a Chord diagram, i.e., a diagram that shows relationship among a group of items (or migration data).

In this specific example we imagine to have a dataframe containing data about some transictions among Barcelona districts.

```{r eval=TRUE, echo=FALSE}
#  setwd("/Users/matteo.manca/Dropbox/Sync/Research-Projects/dataviz/ChordDiagram")
```

#### The dataset is stored in a csv file and has the following format:
```{r eval=TRUE, echo=FALSE}
  input_data =  read.csv(file = "chord_data.csv", header = T, sep = ',')
  head(input_data)
```

#### Function to generate the diagram
```{r eval=TRUE}
  createChordDiagram <- function (inputFile, outputFilePlot){ #, outputFileData
  
    library(circlize)
    library(plyr)
    set.seed(999)
    
    migration_file <- inputFile
    migration <- read.csv(migration_file, sep = ',', header = TRUE)
    
    head(migration)
    
    g = chordDiagram(migration) 
    print(g)
    
    pdf(outputFilePlot) # save in pdf
    
    g = chordDiagram(migration) 
    print(g)
    
    circos.clear()
    dev.off()
}

```


#### Create diagram and save it in the chord_plot.pdf file

```{r eval=TRUE}
createChordDiagram(inputFile = 'chord_data.csv', outputFilePlot = 'chord_plot.pdf')
```
